Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-06 lloveras_2020_v2.tex
nuevos ajustes del referi

\noindent 
{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}

@@

{To characterize the DEMT results in different magnetic structures, we traced} $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model. For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected. For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
\caption{\emph{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). \emph{Bottom panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, red, {magenta and cyan} color, respectively.}}
\label{rpoint_demt}
\end{center}
\end{figure}

{For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}. Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III. On the other hand, of the {$\approx 44000$} legs selected for CR-2208, 10\% are type 0, 43\% are type I, 30\% are type II and 17\% type III.

@@

Figure \ref{gradt_demt} shows frequency histograms {of $\dr\Tm$} for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs. We will return to this point in the \edit{Conclusions}.}

@@

{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by leg type}. From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}. From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$ {(at the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}

@@

{{Several details from Figure \ref{perf_lat} are \edit{worth highlighted}. Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. \edit{Lastly, the DEMT} electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend. {For comparison,\edit{$B_r$ in the CHs increases} from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_conajuste.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_conajuste.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (red), II (magenta), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\section{{Discussion and Conclusions}}\label{discu}

We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208. The former belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24. The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme (Section \ref{demt}). The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).

{Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types. {Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I). {Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}

\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt. \del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.}

@@

{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops. We found characteristic values in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$. A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).}

Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines. The detailed comparison shown in this work can be summarized as follows. For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$. {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works. \citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}

{The overall better match of the results of the current version of the AWSoM model compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}. Note also that the simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps. This is likely the cause \edit{of a more accurate match} to the DEMT reconstructions in the case of CR-2208.}

\del{Within the {quantitative match between both {models summarized} in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}. }For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend. This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles.} {These unphysical characteristics of the results of the AWSoM model in the \edit{range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes. This will \edit{be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.}

>>>>

\noindent 
{where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {\edit{For} any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}

@@

\del{To characterize the DEMT results in different magnetic structures, we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model. For both rotations, all legs that meet the criteria listed in Section \ref{trace} were selected. For each leg, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}. {As a result, the electron density $N_0(r=1.0\,\mrsun)$ and scale height $\lN$ were computed for each leg, as well as the temperature gradient $\dr\Tm$, and the height-averaged (along the leg) {electron temperature} $\aTm$.}}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2082_demt_paper_test_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Grispoint_2208_demt_paper_test_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_conajuste_doble_error_Rpoint-map.pdf}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_conajuste_doble_error_Rpoint-map.pdf}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_full_conajuste_doble_errorhighpoints.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_full_conajuste_doble_errorhighpoints.eps}
\caption{{Top panels:} {latitude-longitude location at heliocentric height $r=1.105\,\mrsun$ of all open (grey color) and closed (black color) traced field line legs for which criterion (i) of Section \ref{trace} is met, for both CR-2082 (left) and CR-2208 (right). {Mid panels}: latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. {The location of} type 0, I, II and III legs {is shown} in blue, \edit{orange, red and cyan} color, respectively.}\edit{Bottom panels: histograms of the latitudinal distribution at $r=1.105\,\mrsun$ of the selected legs.}}
\label{rpoint_demt}
\end{center}
\end{figure}

{For both rotations, the top panels of Figure \ref{rpoint_demt} show the latitude-longitude location (at heliocentric height $r=1.105\,\mrsun$) of all traced field line legs for which criterion (i) of Section \ref{trace} is met. Open legs are indicated in gray color and closed ones in black color. \del{For each leg, the fits to tomografic temperature and density were applied, as given by Equations \ref{Nfit}-\ref{Tfit}.} Considering the DEMT data points and the resulting fits along each leg, the bottom panels of Figure \ref{rpoint_demt} show the latitude-longitude location of the subset for which also both criteria (ii) and (iii) of Section \ref{trace} are met. Using a four-color code, type 0, I, II and III legs are shown in blue, red, {magenta and cyan} color, respectively.} Of the {$\approx 44000$} legs selected for CR-2082, 20\% are type 0, 31\% are type I, 23\% are type II and 26\% type III. On the other hand, of the \edit{$\approx 50000$} legs selected for CR-2208, 10\% are type 0, \edit{38}\% are type I, \edit{27}\% are type II and \edit{25}\% type III.

@@

Figure \ref{gradt_demt} shows frequency histograms of $\dr\Tm$ for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, the median value of the temperature radial gradient is \edit{${\rm Md}\left(\dr\Tm\right) \approx -2.2$, $+2.3$, $+2.4$ and $+2.3\,\MK/\mrsun$ for legs of type 0, I, II and III, respectively.}
\del{
{The notable difference between both rotations is the characteristic {value ${\rm Md}\left(\dr\Tm\right)\approx +4.5\,\MK/\mrsun$} for legs of type III for CR-2208. This is related to the relatively larger values of the score $R$ for the CH of CR-2208, making the DEMT results based on AIA data less reliable in the CHs. We will return to this point in the {Conclusions}.}
}

@@

{For both rotations, Figure \ref{histos_fulldemt} shows, in a statistical fashion, the DEMT results traced along field lines discriminated by leg type}. From top to bottom {results are shown for} type 0 to type III {legs}{, respectively}. From left to right the panels show the statistical distribution of the electron density value $\NCB \equiv \sqravgN(r=1.055)$ \del{(at the lowest height where the AWSoM results are consistent with coronal conditions)}, $\lN$ {and} $\aTm$, {with the median value $m$ indicated in each plot}.

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. \edit{For} type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, this affects only the smallest sized loops of the type 0, and it is likely due \edit{to emission out of the instrumental sensitivity range}. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}

@@

{Several details from Figure \ref{perf_lat} are \edit{worth highlighted}. Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both rotations the models agree within $\approx 15\%$ at all latitudes \del{of the streamer belt, showing larger discrepancies in the CHs}. Secondly, for both rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. \edit{Lastly, the DEMT} electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), while the AWSoM model shows the opposite trend. {For comparison,\edit{$B_r$ in the CHs increases} from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_conajuste.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_conajuste.eps}
\caption{{Average fits to $\Ne(r)$ (left panels) and $T_e(r)$ (right panels) for legs of {type I (\edit{orange}), II (\edit{red}), and III (cyan)}, for CR-2082 (top panels) and CR-2208 (bottom panels). Solid lines correspond to DEMT results while dashed lines correspond to AWSoM results.}}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\section{{Discussion and Conclusions}}\label{discu} 
\del{
We carried out the 3D DEMT reconstruction and MHD modeling of the inner solar corona for two target rotations, CR-2082 and CR-2208. The former belongs to the deep minimum epoch between SCs 23 and 24, while the latter belongs to the end of the declining phase of SC 24. The present work introduces two improvements in the implementation of DEMT, namely the use of only off-limb data in the EUV images, and the inclusion of a 3D regularization scheme (Section \ref{demt}). The MHD model used is here the latest version of the AWSoM component of the SWMF suite  (Section \ref{awsom}).
Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types. {Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I). {Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}

\del{Concerning the DEMT reconstructions, Figure \ref{rpoint_demt} shows that, for both rotations,} \edit{Magnetic} field lines of type 0, I and II are associated with increasingly outer {layers} of the equatorial streamer belt. \del{Figure \ref{histos_fulldemt} and Table \ref{tabla_demt} show in 3D quantitative detail how} \edit{These progressively} outer magnetic structures exhibit decreasing coronal base density, increasing density scale height, and increasing electron temperature. For both rotations we find that down legs populate the low latitudes of the streamer belt, while up legs dominate its mid-latitudes. \del{DIEGO: esto no es cierto, es nuestra definicion y no un resultado.} Also, in the case of CR-2082 the fraction of down legs is significantly larger than for CR-2208. These findings are consistent with previous studies by \citet{huang_2012} and \citet{nuevo_2013}. In the case of the latter, they include in their analysis target CR-2081, which is a rotation almost identical to our target CR-2082. Our results for target CR-2082 compare very well with those of \citet{nuevo_2015} and \citet{lloveras_2017} for target CR-2081. As our study uses the improved version of the DEMT technique, such comparison provided a consistency \edit{check.} \del{for the changes implemented in the DEMT technique.}

@@

{\del{In the streamer belt region we combined the DEMT results and the AWSoM magnetic model to infer the energy input flux $\phi_h$ at the coronal base required to maintain stable coronal loops. We found characteristic values in the range \\}
\edit{The energy input flux $\phi_h$ at the coronal base, required to maintain stable coronal loops, is in the range} $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Based on spectroscopic data of the EIS instrument in quiet-Sun regions \citet{hahn_2014} showed that, if the observed non-thermal broadening are assigned to Alfvén waves, their energy flux at the coronal base is estimated to be in the range $\approx 1.5-2.5\times 10^5\,\erg\,\cminvs\,\s^{-1}$. A large fraction of the coronal base energy input flux $\phi_h$ estimated in this work, or even its totality, could then be accounted for by Alfvén waves (see the discussion in \citealt{maccormack_2017}).}

\del{
Results of the AWSoM model {were compared} to those of the DEMT reconstructions {in the range of coronal heights simultaneously covered by both models, namely $\approx 1.05-1.20\,\mrsun$.} In its current implementation, the AWSoM model can not reproduce down loops (type 0), so the comparison is restricted to type I, II and III field lines.} The detailed comparison shown in this work can be summarized as follows. For CR-2082, the electron density of both models agree within $\approx 20\%$ {in most regions}, while for CR-2208 the agreement is within $\approx 5\%$. {The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much.} In the case of the electron temperature, both models agree within $\approx 10-15\%$ in all regions, for both rotations\del{, with larger discrepancies in the CHs.} This level of agreement between both models {(within or slightly beyond the uncertainty level of DEMT results)} is considerably better than that reported in previous works. \citet{jin_2012} and \citet{oran_2015}{, who used previous versions of the AWSoM model,} reported electron density values of the AWSoM model {differing by $\approx 50\%$ compared to the DEMT reconstructions, both in the equatorial streamer and CH regions.}

{The overall better match of the results of the current version of the AWSoM model compared to DEMT reconstructions is partly due to the improved energy partitioning scheme of the model, described in Section \ref{awsom}. \edit{The} simulation of CR-2082 used GONG maps as boundary condition, while the simulation of CR-2208 used the improved ADAPT-GONG maps. This is likely the cause \edit{of a more accurate match} to the DEMT reconstructions in the case of CR-2208.}

\del{Within the quantitative match between both models summarized in the previous paragraph, there are some qualitative agreements and {disagreements worth noticing}. }For both rotations, the AWSoM model reproduces the relatively lower temperatures found by DEMT to characterize the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. On the other hand, while the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density {(physically expected in transitioning from magnetically closed to open regions)}, this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Also, while the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two rotations), {as expected in transitioning from the source region of the slow to the fast component of the solar wind}, the AWSoM model shows the opposite trend. This behavior is notoriously opposite to that reported in the AWSoM model version used by \citet{oran_2015}, in which the electron density decreases from the open/closed boundary towards the poles. These unphysical characteristics of the results of the AWSoM model in the \edit{range} of low heights analysed here ($r\lesssim 1.2\,\mrsun$), may be attributed to the less reliable values of $B_r$ provided by both the GONG and ADAPT-GONG maps at subpolar latitudes. This will \edit{be investigated} in a follow up article focusing on the current deep minimum epoch, during which the large-scale corona shows the simplest possible structure.
